A Spatial AR System for Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-14 paper/elsarticle/elsarticle-template.tex
paper

%% Group authors per affiliation:
\author{Michael Horn\'{a}\v{c}ek}\corref{mycorrespondingauthor}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{michael.hornacek@tuwien.ac.at}
\author{Hans K\"{u}ffner-McCauley}
\author{Majesa Trimmel}
\author{Patrick Rupprecht}
\author{Sebastian Schlund}
\address{Human Centered Cyber Physical Production and Assembly Systems, Institute for Management Sciences, TU Vienna, Austria}

@@

We propose a spatial AR system for planar scenes that produces the effect of keystone correction analytically. Our system does so in a manner that facilitates placement by enabling intuitively placing the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera facing downwards towards the scene plane, and reasoning about the dimensions of the projected augmentations in metric terms. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling factory floor augmentation exceeding the bounds of the projector's own immediate field of view, using only a single projector.
\end{abstract}

@@

Augmented reality (AR) \cite{van2010survey,zhou2008trends} promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene \cite{schlund2018moglichkeiten,masood2019augmented,gattullo2019towards,rupprecht2020information,Rupprecht2021}, potentially reducing or altogether doing away with the need for workers to refer to instructions in paper form or on a screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed using some form of head-mounted display. Reliance on head-mounted displays, however, has two adverse consequences: (i) a head-mounted display must be worn by each individual wishing to view the augmentation, and (ii) such a head-mounted display---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. \textit{Spatial} AR is a form of augmented reality carried out not by embedding the augmentation in an image of the scene as with head-mounted displays, but by projection to the scene itself \cite{bimber2019spatial}, thus eliminating both aforementioned problems. Yet considering for the moment a planar surface to be augmented, unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular; more generally, they will instead appear trapezoidal (i.e., the projected image will appear distorted). Such distortions can be eliminated by carrying out a cumbersome manual process called keystone correction to appropriately warp the image to be projected, often using software bundled with the projector.

@@

We evaluate our approach by augmenting 15 locations across the floorspace at the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Vienna, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. We contrast our approach with a baseline approach involving manual keystone correction, by aiming with both approaches to place the same image for each location aligned with the principal axes of the floorspace, absent of projective distortions, and with the same metric dimensions (50~cm~$\times$~31.25~cm\footnote{The dimensions in pixels of the image we project are 960~pixels~$\times$~600~pixels; we chose for our experiments to set the projected metric length of the horizontal axis of the image to 50~cm, which implies 31.25~cm for the vertical axis.}). All experiments were carried out by the same technician, experienced in both approaches.

>>>>

%% Group authors per affiliation:
\author{Michael Horn\'{a}\v{c}ek}\corref{mycorrespondingauthor}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{michael.hornacek@tuwien.ac.at}
\author{Hans K\"{u}ffner-McCauley}
\author{Majesa Trimmel}
\author{Patrick Rupprecht}
\author{Sebastian Schlund}
\address{Human Centered Cyber Physical Production and Assembly Systems, Institute for Management Sciences, TU Wien, Vienna, Austria}

@@

We propose a spatial AR system for planar scenes that produces the effect of keystone correction analytically. Our system does so in a manner that facilitates placement of augmentations in the scene by enabling intuitively placing the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera facing downwards towards the scene plane, and reasoning about the dimensions of the projected augmentations in metric terms. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling factory floor augmentation exceeding the bounds of the projector's own immediate field of view, using only a single projector.
\end{abstract}

@@

Augmented reality (AR) \cite{van2010survey,zhou2008trends} promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene \cite{schlund2018moglichkeiten,masood2019augmented,gattullo2019towards,rupprecht2020information,Rupprecht2021}, potentially reducing or altogether doing away with the need for workers to refer to instructions in paper form or on a screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed using some form of head-mounted display. Reliance on head-mounted displays, however, has two adverse consequences: (i) a head-mounted display must be worn by each individual wishing to view the augmentation, and (ii) such a head-mounted display---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. \textit{Spatial} AR\cite{bimber2019spatial} is a form of augmented reality carried out not by embedding the augmentation in an image of the scene as with head-mounted displays, but by projection to the scene itself , thus eliminating both aforementioned problems. Yet considering for the moment a planar surface to be augmented, unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular; more generally, they will instead appear trapezoidal (i.e., the projected image will appear distorted). Such distortions can be eliminated by carrying out a cumbersome manual process called keystone correction to appropriately warp the image to be projected, often using software bundled with the projector.

@@

We evaluate our approach by augmenting 15 locations across the floorspace at the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Wien, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. We contrast our approach with a baseline approach involving manual keystone correction, by aiming with both approaches to place the same image for each location aligned with the principal axes of the floorspace, absent of projective distortions, and with the same metric dimensions (50~cm~$\times$~31.25~cm\footnote{The dimensions in pixels of the image we project are 960~pixels~$\times$~600~pixels; we chose for our experiments to set the projected metric length of the horizontal axis of the image to 50~cm, which implies 31.25~cm for the vertical axis.}). All experiments were carried out by the same technician, experienced in both approaches.
